---
title: "Data 607 Week 9 Assignment"
author: "Justin Hsi"
date: "3/26/2020"
output:
  html_document: default
  pdf_document: default
---


```{r setup, include=TRUE, cache = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# We need these packages
library(tidyverse)
library(jsonlite)
library(knitr)
```

Overview:
We are tasked with choosing one of the New York Times's APIs to read in JSON data and transform it into an R dataframe.First we need to get an api key from [link](https://developer.nytimes.com/apis)

Next we can use GET methods with the API

```{r}
nyt_api_key = Sys.getenv("nyt_api_key")
q = paste("http://api.nytimes.com/svc/semantic/v2/concept/name/nytd_des/Baseball.json?fields=all&api-key=",nyt_api_key)
x = fromJSON(q, flatten=TRUE)
```



```{r}
kable(x[5])
```

Conclusions:
We are able to use the NYT API to query data and read into R dataframes. It looks like the semantic API is not straightforward to interpret, nor is it obvious to see how the data may need to be tidied.
