---
title: "Data 607 Week 7 Assignment"
author: "Justin Hsi"
date: "3/15/2020"
output:
  html_document: default
  pdf_document: default
---


```{r setup, include=TRUE, cache = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# We need these packages
library(RCurl)
library(XML)
library(jsonlite)
library(knitr)
```

Overview:
We are tasked with creating an HTML, XML, and JSON of 3 books from a favorite subject and loading these into R and verifying the data frames are the same.


First read html

```{r}
html_url = "https://raw.githubusercontent.com/jmhsi/DATA_607/master/books.html"
html_cont = getURLContent(html_url)
books_html = readHTMLTable(html_cont)[[1]]
kable(books_html)
```

Next read XML

```{r}
xml_url = "https://raw.githubusercontent.com/jmhsi/DATA_607/master/books.xml"
xml_cont = getURLContent(xml_url)
books_xml = xmlToDataFrame(xmlParse(xml_cont))
kable(books_xml)
```

Finally read Json

```{r}
json_url = "https://raw.githubusercontent.com/jmhsi/DATA_607/master/books.json"
books_json = fromJSON(json_url)[[1]]
kable(books_json)
```

Json already looks different (author is being interpreted as a character vector when there are more than 2). Let us actually compare.

```{r}
all.equal(books_html, books_xml) # the html and xml are the same
all.equal(books_json, books_xml) # but the json is not

# lets look at structure of each
str(books_html)
str(books_xml)
str(books_json)
```

Conclusions:
We see that the XML and HTML are identical. When loaded into dataframes they turn all the variables into factors by default. For json, we see that the variables are typed as we'd expect them to be with characters, ints, etc. In this case, it may be more desirable to work with JSON as it has tried to infer dtypes which may cut out one step of our data cleaning process. 
