---
title: "Data 607 Week 7 Assignment"
author: "Justin Hsi"
date: "3/15/2020"
output:
  html_document: default
  pdf_document: default
---


```{r setup, include=False}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# We need these packages
library(RCurl)
```

Overview:
We are tasked with creating an HTML, XML, and JSON of 3 books from a favorite subject and loading these into R and verifying the data frames are the same.


#1
First read the html
```{r}
html_url = "https://raw.githubusercontent.com/jmhsi/DATA_607/master/books.html"
html_cont = getURLContent(html_url)
#books_html = readHTMLTable(htmlContent)[[1]]

```

#2
Read in csv from github, fill in two missing airline values
```{r}
df = read_csv('https://raw.githubusercontent.com/jmhsi/DATA_607/master/flights.csv')
# reshaped = cast(ratings_table_2, names ~ movies, value='ratings')
# fill missing Airline lines
df[2,1] = 'Alaska'
df[5,1] = 'AM WEST'
kable(df, caption='Data from csv with added airline information')
```

We use pivot_longer to turn columns 3:7 into a single column called location
```{r}
df = df %>% pivot_longer(cols = 3:7, names_to = 'location', values_to ='counts', values_drop_na = TRUE)
colnames(df) = c('airline', 'status', 'location', 'counts')
kable(df, caption='Pivot longer the location column')
```

Pivot the status column into 2 columns since we are going to be doing analysis about delayed vs on time.
```{r}
df = df %>% pivot_wider(names_from=status, values_from=counts) %>% arrange(airline)
kable(df, caption='Pivot wider the status column')
```

#3
Perform analysis to compare the arrival delays for the two airlines.
Make totals column to find percents with.
```{r}
df$total_flights = df$`on time` + df$delayed
df$pct_on_time = df$`on time`/df$total_flights
df$pct_delayed = df$delayed/df$total_flights
df = df %>% pivot_longer(cols = 6:7, names_to = 'pct_status', values_to = 'pct')
```

```{r}
delays_df = df %>% filter(pct_status == 'pct_delayed')
ontime_df = df %>% filter(pct_status == 'pct_on_time')
alaska_df = df %>% pivot_wider(names_from = pct_status, values_from = pct) %>% filter(airline == 'Alaska')
amwest_df = df %>% pivot_wider(names_from = pct_status, values_from = pct) %>% filter(airline == 'AM WEST')
alaska_overall_delay_pct = sum(alaska_df$delayed)/sum(alaska_df$total_flights)
amwest_overall_delay_pct = sum(amwest_df$delayed)/sum(amwest_df$total_flights)
ggplot(delays_df, aes(x = location, y = pct, fill = airline)) + geom_bar(stat = 'identity', position = 'dodge') + ylab("pct_delays") + annotate("text", x = 2, y = .28, label = paste("Overall Alaska Delay Rate:", alaska_overall_delay_pct)) +
annotate("text", x = 2.1, y = .25, label = paste("Overall AMWEST Delay Rate:", amwest_overall_delay_pct))
```

Conclusions:
We can see across all locations that Alaska has a smaller percentage of delayed arrivals.
However, this contrasts with the overall delay rate, which shows that AMWEST actually
has a lower overall percent of delayed arrivals to total flights. So depending on the
context, our determination of which airline has more delays can change.
